\input{header}
\begin{document}
\section{Reduced problem (?)}
Let $K$ be an unweighted clique where each edge has importance score
(possibility: leverage score) $< \eps$.
Here, the importance score is taken with respect to a graph $G$
containing $K$.

Then use $O(|V(K)|)$ edges to find some good approximation for $G$.
Additionally, having a nice bound on how $K$ approximates $G$ could be
nice.

However, it seems that in some cases, $x^T L_K x$ and $x^T L_G x$ are
the same, so approximating $L_K$ alone may not work well. One example of
this is if you have two cliques $A$ and $B$, and a vertex $v$ between
them connected to $\eps^{-1}$ elements of $A$ and $\eps^{-1}$ elements
of $B$. Each edge has leverage score $< O(\eps)$ (calculate effective
resistances to check). But the clique formed by Schur complementing out
$v$ can easily contain the entire quadratic form, if the vector input is
$1$ on one clique and $-1$ on the other clique.

But you would only be allowed one matching.

\section{Line}
Suppose I have a line graph $G$. I split each edge into $\eps^{-1}$
copies, and try to Schur complement out any vertex $v$.

Then I am left with the following task: Use $\eps^{-1}$ edges to
sparsify the clique between $v-1$ and $v+1$. That's a lot of edges, and
a small number of vertices.
\section{Star}
\section{Failed attempt number 2}
Suppose I have the following Lemma, which is very similar to Lemma 7.6
in Chu et. al. (CGPSSW 18).

\begin{lemma} Let $K$ be a collection of bicliques. Then $K$ can be 
  $\epsilon$ sketched with
  $O(n \eps^{-1} + n(K) \eps^{-0.5})$ edges.
\end{lemma}
Here, $n(K)$ is the total number of vertices in a collection of
bi-cliques.

Now: suppose we wanted to take a vertex $v$ with $d$ multi-edges
adjacent to $v$. Here, $d$ can be larger than $n$.

If each of the multi-edges have leverage score less than $\eps$, then
the resulting (weighted) clique obtained via the Schur complement
has a total leverage score less than $d\eps$.

Let this clique be $K$. Then since 
\[ L_G^{\dag/2} L_K L_G^{\dag/2} \leq d\eps,\]

then 

\[x^T L_K x \leq d\eps x^T L_G x \]

Er, that's a real bad bound. I'd hoped it to be $d\eps / n$.
\end{document}
