\input{header}
\begin{document}
This note is a lot shorter than it used to be, since I made a huge
fuckup that I recently caught. (The fuckup was that I thought that you
could split the initial graph into buckets of edges by power of 2, and
take a schur complement for each bucket.)

\section{Tim's understanding in a small nutshell.}
My understanding of KS'16 is: you take a graph, split edges into
multi-edges so that each edge has low leverage score (approximately
$\eps^2$, plus some polylogs). Then for any
vertex, you can Schur-complement out the vertex, and subsample the
clique with exactly as many edges as were pivoted out.

(Tim's note: I realize I am confused here. My understanding is that you
split edges until the leverage score is bounded above by $\eps^2$. But
Alogrithm 1 in KS'16 happens to argue for splitting every single edge
into $\eps^-2$ copies, which seems like not the right thing to do.)

This operation happens to only lower the leverage score, by a factor of
2 (I think). Thus bounds on leverage scores are kept the same. Then, a
Matrix Martingale allows you to get bounds on the quality of the
approximate sparse Cholesky decomposition. (I must embarassingly admit
that I'm still not super familiar with how the Matrix Martingale works,
or what approximate sparse Cholesky decomposition is.)

\section{Onto $\rho = \eps^-1$.}

Let's pretend we had a magic box to do a degree preserving sparsify on
the clique after Schur Complementing. 

I ran the following thought experiment: Suppose that we had a
multi-graph $G$ such that clique $K$ is a subgraph of $G$. Suppose we
additionally have the properties that clique $K$ has:
\begin{enumerate}
  \item Unit weight edges
  \item Each edge has a leverage score $<\eps$.
\end{enumerate}

Suppose magically, that we have a box that gives us a randomized graph $K'$
supported on the edges of $K$, where

\[\var{}{x^T K' x} = \left(\sum_{u \in K} x_u^2\right)^2.\]

This is the variance of $x^T A_{K'} x$ if you just flipped a coin on
every edge in clique $K$,  where $A_{K'}$ is the adjacency matrix for
$K'$. This is a really weak estimate (probably up to many multiplicative
log factors) of the variance of any degree-preserving box that gives
$K'$.

Thus, we would then like to prove that: if $K$ is a clique such that
every edge in $K$ is unit weight, and has leverage score less than
$\eps$, then 

\[ \left(\sum_{u \in K} x_u^2 \right)^2 \]

is bounded above by

$ \eps^2$.

Unforutnately, I don't really know how to translate low leverage score
into low variance.

\end{document}
