\input{header}
\begin{document}

\title{Title}
\author{
  Timothy Chu \\
  Carnegie Mellon University\\
  \texttt{tzchu@andrew.cmu.edu}
}

\setcounter{page}{0}
\maketitle
\thispagestyle{empty}
\begin{abstract}
Madry '16 (Computing Maximum Flow with Augmenting Electric FlowS)
presents a $O(m^{10/7}U^{1/7})$ time algorithm for computing max
flows. He does so via an `interior point method', by maintainig a
primal flow and a 'dual' (which seems to be an embedding into a line.
What is the dual of the max flow, and why is it line embeddable?). 

He maintains this feasible flow by finding an electrical flow with
some resistor setting built from the residual flow (large resistor if
low residual flow), and adds a small multiple of this electric flow to
the actual flow. Then he uses some mysterious cycle-updating trick to
make sure the primal and dual are 'well compled' (or as close to it as
they can be), whatever this means.

Madry maintains the dual for the purpose of helping his
preconditioninng arcs idea, which
is designed to make each step make some progress. But the
math here, as with all optimization, is a large large mystery. The
dual is apparently some kind of certificate that a demand is feasible,
but it's not clear when a demand would not be feasible given
augmenting-paths-based solutions.

Why does this work? It really seems like it should not. I don't have
any reason to believe the math works out.
\end{abstract}

\clearpage
\bibliographystyle{alpha}
\bibliography{refs}
\begin{appendix}
\end{appendix}
\end{document}
