\input{header}
\begin{document}

\title{Title}
\author{
  Timothy Chu \\
  Carnegie Mellon University\\
  \texttt{tzchu@andrew.cmu.edu}
}

\setcounter{page}{0}
\maketitle
\thispagestyle{empty}
\begin{abstract}
We explore the idea of a graph manifold, and lay down some theorems
we'd like to prove.
\end{abstract}
\clearpage
Define a $F$-graph manifold, where $F$ is a family of graphs (possibly
infinite cardinality), each graph having a marked point. We say that $G$ is an
$F$-graph manifold if for each point $v$ in $G$, there exists a set of
vertices $V$ containing $v$ such that the induced graph on $V$ is in
$F$, and $v$ is the marked point.

We can toggle whether we want the entire neighbor set of $v$ to be
in $V$ or not. The reasons we might want to require this is because
otherwise, ten squares joined at a point is a square-graph manifold,
and it is unclear whether we want to allow that.

Under this notion, treating $F$ as a $q$ by $q$ square gives the
standard mesh manifolds for $2$ dimensions. Treating $f$ as the $k$
point start is the $k$-ary binary tree. But low degree expanders are
also $k$-ary tree graph manifolds under this definition. Tree to
expander is like plane to sphere. (This link and definition are
motivated by Wu'19).

I wonder what kinds of theorems you can prove? You can probably also
create definitions like graph crystals (some kind of regularity
structure in the graph, depending only on the graph and not some
ambient space). It seems like one could theoretically redo
crystallography with this.

But what theorems could be interesting?

\bibliographystyle{alpha}
\bibliography{refs}
\begin{appendix}
\end{appendix}
\end{document}
