\begin{abstract}
Hitting times of random walks are widely studied asymmetric measures in
combinatorics and data mining. The most common symmetrization of
hitting times are known as commute times, proportional to the
effective resistance. It is known that commute times have
properties that are considered undesirable in large scale machine
learning.  For example, a ball of radius $r$ in the commute-time
metric can be disconnected.

In this paper, we propose an alternative symmetrization of
hitting times with the property that any ball in this
symmetrization is identical to some ball in the hitting time
measure around $a$: that is, the ball $\{ x : H(x, a) < r \}$, where $H(x, a)$ is
the hitting time from $x$ to $a$ and $r$ is any scalar.
This property ensures that balls in our alternative
symmetrization form connected components.
This symmterized notion of hitting times has desirable properties
when computing Voronoi cells, including the property that in any
Voronoi diagram with two sites, each cell is connected.

It is known that for large-scale random geometric graphs, the
hitting times capture only local properties of the graph: $H(a,b)
\sim \frac{1}{d_b}$ as the number of vertices get large.
Critically, our symmetrization of hitting times avoids this
problem, and captures the global structure of the graph.  
Our analysis and construction is not restricted to only hitting time
measures, and we will present criteria for when any measure can
be symmetrized in this fashion.
\end{abstract}
