\input{header}
\begin{document}
Reductions; General graph to a diameter $ D = O(\log n)$ graph.

\begin{theorem}
  Low diameter decomposition: It takes linear time (single
  processor) to decompose into $O(\log n)$ size pieces, in $O(m + n\og
  n)$ time, constant fraction of edges.
\end{theorem}

Note: we only need $O(1 - 1/\log n)$ edges in cycles.

Assume small diameter: Cycle Cover. ($O(\log n)$ congestion, every edge
is covered).

\begin{theorem} Parter '18. Cycle cover doable with cycles length at
  most $D$, every edge in at most $C$ cycles. Here, $C = polylog$ and $D
  = \log$. This can be done in $O(m)$ time. (Bridgeless graphs).
\end{theorem}

Everything except time is covered in Parter '18. 
Parter '18: how to find a cycle cover. Divide the line into blocks. The
number of non-tree endpoints-of-edges is exactly $100$.  (Call this the
non-tree degree). The non-tree of a block is $50 \leq 100$ by
construction. (Can ignore over-heavy singletons).

When you contract a non-tree edge (let $M$ be non-tree edges), contract
the blocks (?), then this graph counting self loops and all that, will
have $M /50 \leq x \leq M / 100$ nodes and $M$ edges.

In this contracted graph, can find the $O(\log n)$ size cycles. Goran
has a bug!

Algorithm part 1: Take any spanning tree (of low depth). (Line not of
low depth?)

\section{Parter's Algorithm.}
For any graph, take a low diameter spanning tree by BFSing on it. Then,
contract the graph based on a pre-order traversal. Take successive
subtrees of graphs rooted at the vertex in the pre-order traversal, and
start including them in each "part" until the number of non-tree edges
leaving them is between 50 and 100.

\end{document}
